Central chiller plants remain a major source of electricity consumption in continuously operated cooling systems, yet much of the recent literature emphasizes simulation-based tuning, model predictive control, or facility-specific digital twins. This paper develops a reproducible day-ahead mixed-integer linear programming framework for the robust scheduling of a heterogeneous multi-chiller plant with chilled-water storage, chilled-water pumps, condenser-water pumps, and cooling-tower auxiliaries. The formulation is implemented in Pyomo and combines explicit unit commitment, piecewise-linear chiller efficiency curves, storage dynamics, and a Bertsimas-Sim-style budgeted robust treatment of cooling-load and tariff uncertainty. We evaluate the framework on a semi-synthetic 24-hour benchmark plant with three large chillers, one small chiller, and time-of-use electricity pricing. Relative to the lowest-cost deterministic schedule with storage, the robust formulation with storage increases total operating cost from 5584.7 to 6002.1 while reducing the out-of-sample mean cooling shortfall from 740.3~kWh to 66.5~kWh and the correlated-stress mean shortfall from 528.0~kWh to 23.0~kWh. Compared with a robust formulation without storage, thermal storage further lowers total cost from 6128.2 to 6002.1 without degrading the shortage metric. Additional ablations show that increasing the uncertainty budget systematically trades operating cost for resilience and that larger storage capacity improves economic performance. We frame the study as a reproducible proof-of-concept benchmark rather than a field-validated deployment study.
