\section{Introduction}

Central cooling plants and multi-chiller systems remain among the most electricity-intensive assets in large commercial, industrial, and mission-critical facilities. Their operation is complicated by heterogeneous chiller efficiencies, auxiliary pumping and heat-rejection loads, time-varying tariffs, and uncertain cooling demand. In practice, many sites still rely on rule-based sequencing, static setpoints, or simulator-assisted retuning, which often leaves non-trivial system-level savings unrealized.

Recent work shows that coordinated plant-level optimization can produce meaningful gains. Modelica-based global optimization and calibrated digital twins have revealed substantial savings in industrial and data-center cooling plants \citep{niu2023global,bai2024modelica,fu2019equation,kong2025industrial}. In parallel, predictive-control studies have demonstrated the value of jointly dispatching chillers and thermal storage in campuses, airports, and data centers \citep{campos2021dispatch,zhu2023storage,zhao2024mpc,chinde2024airport,lin2025inherent}. However, these strands of work usually emphasize one axis at a time: high-fidelity plant modeling, online MPC, or uncertainty-aware scheduling under simplified plant scope.

This paper focuses on a narrower but practically useful planning problem: \emph{day-ahead scheduling of a heterogeneous multi-chiller plant under coupled load, price, and ambient uncertainty}. The key observation from our literature review is that robust chiller scheduling has been studied before, including systems with chilled-water storage \citep{sadatmohammadi2020robust,saeedi2019robust}. The more defensible gap is therefore not ``robust scheduling'' in isolation. Instead, the gap lies in a reproducible full-plant MILP scaffold that simultaneously captures heterogeneous chiller commitment, auxiliary-equipment coupling, and weather-sensitive efficiency degradation in a form that remains compact enough for broad ablation and paper-ready reproducibility.

We therefore develop an \emph{ambient-aware robust} Pyomo-MILP framework. The model keeps the planning horizon at 24 hourly periods and explicitly represents chillers, chilled-water pumps, condenser-water pumps, cooling-tower auxiliaries, and chilled-water storage. Budgeted uncertainty is used for cooling load and tariff uncertainty, while wet-bulb uncertainty is propagated through conservative linearized chiller-power coefficients and temperature-dependent available-capacity limits. This keeps the formulation MILP-solvable while making the benchmark more physically meaningful than a purely nominal efficiency model.

Our main contributions are:
\begin{enumerate}[leftmargin=1.5em]
    \item We formulate a reproducible full-plant day-ahead MILP for heterogeneous chillers, thermal storage, and auxiliary equipment using explicit unit commitment and piecewise-linear performance surrogates.
    \item We extend the robust scheduling layer beyond load and price uncertainty by introducing \emph{ambient-aware} robustness, which captures wet-bulb-driven efficiency degradation and capacity derating without leaving the MILP regime.
    \item We provide a semi-synthetic benchmark and experiment pipeline with rule-based, deterministic, partially robust, and fully ambient-aware robust baselines, together with ablations on uncertainty budget, storage size, weather robustness, equipment heterogeneity, and auxiliary-equipment modeling.
\end{enumerate}

Empirically, the deterministic MILP with storage remains the cheapest nominally, but it is brittle under uncertainty. The proposed ambient-aware robust formulation incurs a moderate cost premium while sharply reducing both standard out-of-sample shortage and correlated weather-linked stress metrics. We therefore position the framework as a benchmark methodology for planning-oriented cooling optimization rather than as a deployed supervisory controller.

The remainder of the paper is organized as follows. Section~\ref{sec:related} reviews the most relevant strands of chiller-plant optimization. Section~\ref{sec:method} presents the plant model and ambient-aware robust MILP formulation. Section~\ref{sec:experiments} describes the benchmark case and discusses comparative results. Section~\ref{sec:conclusion} concludes with limitations and next steps.
