\section{Related Work}
\label{sec:related}

\paragraph{Global optimization and sequencing of chiller plants.}
Plant-level optimization for chiller systems has long targeted equipment sequencing, setpoint selection, and economic dispatch. Niu et al.~\citep{niu2023global} showed that model-based global optimization can extract savings from an existing 24-hour operating chiller plant without interfering with production. Bai et al.~\citep{bai2024modelica} further highlighted the interaction among sequencing, load allocation, and parameter optimization in heterogeneous multi-chiller systems. More recent practical validation studies continue to show that water-side coordination and subsystem-aware control are key energy-saving levers \citep{kong2025industrial}. These studies strongly motivate system-level optimization, but they are primarily simulation-centric and do not directly emphasize an open, compact, robust MILP implementation for benchmark-style day-ahead planning.

\paragraph{Modelica-based calibration and digital twins.}
Equation-based and object-oriented models have become important for diagnosing plant inefficiencies and assessing candidate operating policies. Fu et al.~\citep{fu2019equation} demonstrated how a calibrated Modelica model can identify hidden control issues and quantify savings in a real data-center cooling system. This line of work is valuable because it supports plant-specific interpretation and richer physics. At the same time, such workflows are often tied to calibration effort, simulator tooling, and site-specific data availability. Our goal is complementary: not to replace digital twins, but to provide a lighter-weight scheduling scaffold that remains transparent and easily extensible across benchmark cases.

\paragraph{Predictive control and storage-coupled cooling.}
Another major line of work develops MPC or learning-enhanced predictive control for cooling plants. Campos et al.~\citep{campos2021dispatch} optimized day-ahead and real-time dispatch of chillers and thermal storage in a campus central plant. Zhu et al.~\citep{zhu2023storage} and Zhao et al.~\citep{zhao2024mpc} studied MPC for multi-chiller data-center cooling with storage or whole-system conservation objectives, while Chinde and Woldekidan~\citep{chinde2024airport} extended predictive dispatch to airport central plants. Lin et al.~\citep{lin2025inherent} recently emphasized the value of inherent cold storage for improving large-plant efficiency. These papers demonstrate the value of storage-aware predictive operation, but they typically rely on online forecasting stacks, receding-horizon re-optimization, or facility-specific dynamic controllers. Our work instead targets the planning layer and asks how much insight can be obtained from a simpler full-plant MILP benchmark.

\paragraph{Robust and stochastic scheduling under uncertainty.}
Uncertainty-aware formulations recognize that load and electricity price are imperfectly known in advance. Saeedi et al.~\citep{saeedi2019robust} and Sadat-Mohammadi et al.~\citep{sadatmohammadi2020robust} are especially relevant because they already show that robust optimization can reduce vulnerability in multi-chiller systems, including plants with chilled-water storage. For this reason, a broad claim of novelty around ``robust multi-chiller scheduling'' would be weak. The more precise gap is that existing robust scheduling studies often abstract away either full-plant auxiliary coupling or ambient-driven performance degradation. Our contribution is therefore positioned as a reproducible \emph{ambient-aware full-plant} benchmark: heterogeneous chiller commitment, storage, pumps, towers, and wet-bulb-sensitive efficiency/capacity effects are kept in one compact MILP workflow.

Overall, the literature supports three takeaways. First, system-level coordination matters. Second, thermal storage can materially improve operating flexibility. Third, uncertainty-aware scheduling is worthwhile, but the treatment of weather-sensitive plant physics remains relatively thin in compact reproducible optimization benchmarks. This paper is intended to fill that narrower gap.
