\section{Appendix}

\subsection{Benchmark Plant Parameters}

Table~\ref{tab:params} lists the main benchmark parameters used in the repository implementation.

\begin{table}[H]
\centering
\caption{Key benchmark parameters.}
\label{tab:params}
\begin{tabular}{ll}
\toprule
Item & Value \\
\midrule
Chiller capacities & 460, 450, 390, 190~kW \\
Minimum part-load ratios & 0.35, 0.35, 0.40, 0.30 \\
Startup costs & 28, 28, 22, 11 \\
Fixed parasitic powers & 24, 24, 20, 8~kW \\
Segment widths & \{90,110,99\}, \{85,110,97.5\}, \{72,96,66\}, \{36,46,51\}~kW \\
Base segment COPs & \{6.35,6.10,5.55\}, \{6.25,6.05,5.50\}, \{5.90,5.70,5.20\}, \{5.75,5.55,5.15\} \\
Storage capacity & 900~kWh \\
Storage charge/discharge limit & 260~kW \\
Storage efficiencies & 0.95 / 0.95 \\
Initial SOC & 450~kWh \\
Load robustness budget $\GammaL$ & 1.4 \\
Price robustness budget $\GammaP$ & 5.0 \\
Unmet-cooling penalty & 100 per kWh \\
OOS sample count & 24 \\
Default solver & HiGHS \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Implementation Notes}

The optimization is implemented in Pyomo and currently solved with a generic MILP backend. The codebase includes:
\begin{itemize}[leftmargin=1.5em]
    \item a semi-synthetic benchmark generator,
    \item deterministic and robust MILP model builders,
    \item a rule-based baseline,
    \item experiment scripts for benchmark and ablation studies, and
    \item automated export of CSV summaries and figure galleries.
\end{itemize}

The benchmark outputs used in this draft were produced from the same repository and are therefore directly reproducible from the accompanying experiment scripts.

\subsection{Omitted Operational Constraints}

The current benchmark does not impose minimum up/down times, ramp-rate limits, or detailed hydraulic state equations. These omissions were intentional to keep the first formulation compact and to isolate the effect of uncertainty-aware scheduling. In a plant-specific deployment study, these constraints should be reinstated and calibrated to equipment specifications.

\subsection{Extended Visual Diagnostics}

In addition to the main-paper figures, the repository exports commitment heatmaps, per-method cooling-balance plots, power-tariff overlays, and storage trajectories for all ablation cases. These diagnostics are useful when inspecting how robustness budgets alter the timing of commitment and the utilization of flexibility resources.
